\documentclass[12pt, conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}
\usepackage{graphicx, wrapfig, subcaption}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage[OT1]{fontenc}
\usepackage{setspace}
% Packages added by me
\usepackage[numbers]{natbib} % Manual of natbib at https://gking.harvard.edu/files/natnotes2.pdf
\usepackage{lipsum}
\usepackage{algorithm}
\usepackage{algpseudocode}

\definecolor{cust-linkcolor}{HTML}{7936ff}

\hypersetup{
    colorlinks=true,
    linkcolor=cust-linkcolor,      
    urlcolor=blue,
    citecolor=red
}

\begin{document}

\title{\textbf{Security Key Authentication for Web Applications}\\
{\small CS588 - Networked Distributed System Security $\mid$ Professor J. Solworth}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Davide Giacomini}
\IEEEauthorblockA{\textit{dept. of Engineering} \\
\textit{University of Illinois at Chicago (UIC)}\\
Chicago (IL), USA \\
giacomini.davide@outlook.com}
\\
% \IEEEauthorblockN{Jake Campbell}
% \IEEEauthorblockA{\textit{dept. of Engineering} \\
% \textit{University of Illinois at Chicago (UIC)}\\
% Chicago (IL), USA \\
% jacobpmcampbell@gmail.com}
}

\maketitle
% Those two lines are useful for numbered pages
\thispagestyle{plain}
\pagestyle{plain}
\onehalfspacing

\begin{abstract}
    The U2F (Universal 2nd Factor Authentication) protocol allows you to send a cryptographic challenge to a device (typically a key fob) owned by the user. A password starts the process, but the digital key is required to gain access. The FIDO U2F protocol was developed in 2014, and since then, the standards have been honed, refined, and updated. More users are growing accustomed to the idea of cryptographic keys. Some even demand this protection to keep their data safe and secure.

    In this brief report I will analyze the advantages of using a security key, and I will dive into the cryptographic protocol harnessed by those devices. Finally, I will present a sample web application, aimed at showing how current libraries and APIs can be exploited to ease the development of security key authentication in web applications.
\end{abstract}

\begin{IEEEkeywords}
    web applications, authentication, security key, FIDO, U2F, security
\end{IEEEkeywords}

\input{sections/introduction.tex}
\input{sections/related-work.tex}
\input{sections/protocol-overview.tex}
\input{sections/implementation.tex}
\input{sections/future.tex}
\input{sections/conclusion.tex}

\vspace{12pt}

\bibliographystyle{unsrtnat}
% Cannot upload \bibliographystyle{IEEEtran} with natbib, don't know why
\bibliography{bibliography}

\end{document}
